Prefetching SPARQL query cacher

### 2016-07-29 dissertation/cache-proxy.tex
names for the analysers

With this constraint, the analysers have been implemented with two
different assumptions of usefulness: In the first case, I try to
capture frequently occurring bound predicates. This is due to the
observation that predicates are often bound, and so predicates that
are common will occur in the future, and therefore, prefetching and
caching results of a triple pattern where the predicate is bound to a
frequently occurring is likely to be beneficial. This is done by
counting the occurrences of predicates, and when the number exceeds a
certain threshold, the prefetcher is instructed to fetch the data.

The second analyser works along a different axis: It tries to find the
triple pattern that, if cached, would provide the greatest cost
benefit. To do so, it will rerun the query planner on the incoming
query while simulating that the results of a certain triple pattern
was in the cache. The simulation will run for \emph{all} triple
patterns that do not already have a cached result. If the cost
reduction of the best plan is larger than a certain limit, the
prefetcher is invoked.

>>>>

With this constraint, the analysers have been implemented with two
different assumptions of usefulness: The first analyser, called
predicate-count, captures frequently occurring bound predicates. This is due to the
observation that predicates are often bound, and so predicates that
are common will occur in the future, and therefore, prefetching and
caching results of a triple pattern where the predicate is bound to a
frequently occurring is likely to be beneficial. This is done by
counting the occurrences of predicates, and when the number exceeds a
certain threshold, the prefetcher is instructed to fetch the data.

The second analyser, named cost-reduction, works along a different
axis: It tries to find the 
triple pattern that, if cached, would provide the greatest cost
benefit. To do so, it will rerun the query planner on the incoming
query while simulating that the results of a certain triple pattern
was in the cache. The simulation will run for \emph{all} triple
patterns that do not already have a cached result. If the cost
reduction of the best plan is larger than a certain limit, the
prefetcher is invoked.
